mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-02-09 EMSOFT2016/thesis.tex
update

%
% File: thesis.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference,compsoc]{IEEEtran}
\bibliographystyle{IEEEtranBST2/IEEEtran}
\usepackage{url}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{listings,jlisting}
\lstset{%
    language={},
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\ttfamily},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compailation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
In the proposed framework, the cyclic handler switching tasks is implemented, and multitasking processing is more easy-to-use than that of mruby on TECS.
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

Although script languages are easy to use and read, their execution time are slower than C language's.
For embedded systems, the real-time properties such as worst-execution time, response time are very important factors.
Therefore, it is difficult to apply the script languages to embedded systems.

mruby on TECS is a component-based framework for running script program \cite{par:mrubyonTECS}.
It is integrated two technologies.
One is mruby, which is a script language for embedded systems \cite{par:mruby}, \cite{url:mruby}.
The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{par:TECS}.
TECS supports to effectively run mruby script language on embedded systems.
mruby on TECS also makes execution time 100 times faster than that of mruby.

This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
mruby on TECS has some problems at present.
One of the problems is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
It can improve the efficiency.
Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by developers.
In addition developers must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
Thus that is a big burden on developers.
Another new feature enables developers to run a multitask programs more easily.
Specifically, a cyclic handler of switching tasks is implemented.
This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.

{\bf Contributions}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
The proposed framework gives the contribution in the following points.
\begin{enumerate}
\item To improve the  work efficiency in software development on mruby on TECS: \mbox{}\\
\ mruby bytecode loader using Bluetooth helps developers develop software.
Developers do not need to insert and pull out an SD card repeatedly and also to restart an OS.
Thus, the software development efficiency is improved.
\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
\ There is a problem in multitasking of the current mruby on TECS.
It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking.
In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
Multitasked programing makes the range of software expand.
\end{enumerate}

{\bf Organization}: The paper is organized as follows.
Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
Section \ref{sec:mruby bytecode loader using Bluetooth} and Section \ref{sec:Multitask} describe the design and implementation of the proposed framework in detail.
Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discuses related work, and then Section \ref{sec:Conclusion} concludes.

\section{Background}
\label{sec:Background}
Figure \ref{fig:proposed} shows a system model of the proposed framework.
The bytecodes are transferred from the host to the target device with Bluetooth.
The RiteVMs and mruby library are assumed to be prepared in advance.
Each bytecode is allocated to a RiteVM, respectively.
Developers can run some bytecodes transferred with Bluetooth in multitask.

@@

mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
In addition, VM (Virtual Machine) mechanism is used in mruby, so mruby programs can run on any operating system as long as VM is implemented.
RiteVM is a VM in mruby, that runs mruby programs.
The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by RiteVM.
The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \caption{Mechanism of mruby/RiteVM}
    \label{fig:mruby}
\end{figure}

@@

    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} description defines {\it entry} ports, {\it call} ports, attributes, and valuables of a {\it celltype}.
        An example of a {\it celltype} description is shown in Figure \ref{celltype}.
        A {\it celltype} name following the keyword {\it celltype} with the prefix ``t" and elements of a {\it celltype} is described.
        To define {\it entry} ports, a {\it signature} such as sMotor, and an {\it entry} port name such as eMotor follow the keyword {\it entry}.
        In the same way, {\it call} ports can be declared.
        Attributes and valuables follow the keyword attr and var respectively.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller{
    call sMotor cMotor;
};
celltype tMotor{
    entry sMotor eMotor;
    attr{
        int32_t attr = 100;
    };
    var{
        int32_t var;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}

    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate {\it cell}s and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name such as tMotor, and a {\it cell} name such as Motor follow the keyword {\it cell}.
        To compose {\it cell}s a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
        In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor{
};
cell tCaller Caller{
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

An mruby-TECS bridge plays a role to call a native program (e.g.,C legacy code) from an mruby program.
The mruby-TECS bridge provides native libraries for mruby.
It also gives TECS components to receive the invocation from an mruby program.
The mruby-TECS bridge is described in more detail bellow.

As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{url:ASP}.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyontecs.pdf}
    \caption{System Model of existing mruby on TECS}
    \label{fig:mrubyontecs}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
    \caption{Specific System Model of the proposed framework}
    \label{fig:system_model}
\end{figure}

@@

\section{mruby Bytecode Loader Using Bluetooth}
\label{sec:mruby bytecode loader using Bluetooth}
This section describes an additional feature of mruby on TECS, mruby bytecode loader using Bluetooth.
In the current system, all binary data including bytecodes are in an SD card.
Developers must insert and pull out the SD card every time the source programs are modified.
It causes a low work efficiency that such a work must be repeated.
mruby bytecode loader using Bluetooth makes the developers' burden decrease.
The work that an SD card is in and out needs to be done just once in the beginning.

@@

One of approaches for multitasking is co-routine.
Co-routine is a cooperative thread, and scheduled by developers with the functions such as {\it resume} and {\it yield}. 
(Ruby co-routine is defined in class Fiber \cite{url:co-routine})
Co-routine is a non-preemptive mulititasking, and does not receive the OS's support because developers have to switch tasks manually.
Co-routine can not take advantege of multi core processing.

Besides, as another method, {\it delay}, a service call of $\mu$ITRON, can be used for multitasking.
This service call delays the execution of the own task for the time of the argument.
In the approach of {\it delay} fubction, developers have to schedule as the same as co-routine.

@@

\subsection{Component of Cyclic Handler}
Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
CyclicHandler {\it cell} configures the cyclic handler based on $\mu$ITRON.
Cyclic handlers based on ITRON are described in detail \cite{par:microITRON}.
The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
{\it rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
The attribute is used as an arguments of {\it rotateReadyQueue}.

Figure \ref{build_cyclic_handler} shows a build description that corresponds to the component diagram shown in Figure \ref{fig:cyclic_handler}.
In the part of CyclicHandler {\it cell}, configurations of a cyclic handler is described such as attribute, cyclicTime and cyclicPhase.
In this case, the cyclic handler is executed when it is generated because the attribute is {\it TA\_STA} that represents the cyclic handler is in an operational state after the creation.
The cyclic handler is executed every one msec.
In another part, the priority of CyclicMain {\it cell} is described.
EV3\_MRUBY\_VM\_PRIORITY defines the priority of mruby tasks.
In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
If developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tCyclicHandler.cdl$>$);}.
This ease comes from component-based development with TECS.

@@

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
Multitasking's execution time is about the same as singletasking's while co-routine takes more time than them to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
Switching tasks's overhead is also evaluated, that is about three $\mu$sec on average.
The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|cccccc}
        & Bluetooth Loader & \shortstack{Call\\C function} & \shortstack{Legacy code of\\embedded system} & VM managenment & \shortstack{Synchronization of\\application} & Co-routine \\ \hline
        Lua \cite{url:Lua}, \cite{par:Lua}           &            & \checkmark & Partially  &            &            & \checkmark \\
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &            & \checkmark \\
        mruby \cite{par:mruby}, \cite{url:mruby}     &            & \checkmark &            &            &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparion}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
eLua \cite{url:eLua},  python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in multi-VM.
Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
%%%%%%%%%%%%%
% Reference %
%%%%%%%%%%%%%
\bibliography{ref}

>>>>

% 
% File: thesis.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference,compsoc]{IEEEtran}
\usepackage{url}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{listings,jlisting}
\lstset{%
    language={},
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\ttfamily},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
In the proposed framework, the cyclic handler switching tasks is implemented, and multitasking processing is more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

Although script languages are easy to use and read, their execution time are slower than C language's.
For embedded systems, the real-time properties such as worst-execution time and response time are very important factors.
Therefore, it is difficult to apply the script languages to embedded systems.

mruby on TECS is a component-based framework for running script program \cite{par:mrubyonTECS}.
It is integrated two technologies.
One is mruby, which is a script language for embedded systems \cite{par:mruby}, \cite{url:mruby}.
The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{par:TECS} \cite{url:TOPPERS}.
mruby on TECS supports to effectively run mruby script language on embedded systems.
mruby on TECS also makes execution time 100 times faster than that of mruby.

This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
mruby on TECS has several problems at present.
One of the problems is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly and the OS should be restarted.
If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and mruby application codes are transferred from a host to a target device by Bluetooth.
It can improve the efficiency.
Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by developers.
In addition developers must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
Thus that is a big burden on developers.
Another new feature enables developers to run multitasking programs more easily.
Specifically, a cyclic handler of switching tasks is implemented.
This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.

{\bf Contributions}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
The proposed framework gives the contribution in the following points.
\begin{enumerate}
\item To improve the  work efficiency in software development on mruby on TECS: \mbox{}\\
\ mruby bytecode loader using Bluetooth helps developers develop software.
Developers do not need to insert and pull out an SD card repeatedly and also to restart an OS.
Thus, the software development efficiency is improved.
\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
\ There is a problem in multitasking of the current mruby on TECS.
It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking.
In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
Synchronization of tasks is implemented.
Multitasked programing makes the range of software expand.
\end{enumerate}

{\bf Organization}: The paper is organized as follows.
Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
Section \ref{sec:mruby bytecode loader using Bluetooth} and Section \ref{sec:Multitask} describe the design and implementation of the proposed framework in detail.
Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discusses related work, and then Section \ref{sec:Conclusion} concludes this paper.

\section{Background}
\label{sec:Background}
Figure \ref{fig:proposed} shows the system model of the proposed framework.
The bytecodes are transferred from the host to the target device with Bluetooth.
The RiteVMs and mruby library are assumed to be prepared in advance.
Each bytecode is allocated to a RiteVM, respectively.
Developers can run bytecodes transferred with Bluetooth in multitask.

@@

mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
In addition, VM (Virtual Machine) mechanism is used in mruby, therefore mruby programs can run on any operating system as long as VM is implemented.
RiteVM is a VM in mruby, that runs mruby programs.
The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by RiteVM.
The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \caption{Mechanism of mruby/RiteVM}
    \label{fig:mruby}
\end{figure}

@@

    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} description defines {\it entry} ports, {\it call} ports, attributes, and valuables of a {\it celltype}.
        An example of a {\it celltype} description is shown in Figure \ref{celltype}.
        A {\it celltype} name following the keyword {\it celltype} with the prefix ``t" and elements of a {\it celltype} is described.
        To define {\it entry} ports, a {\it signature} such as sMotor, and an {\it entry} port name such as eMotor follow the keyword {\it entry}.
        In the same way, {\it call} ports can be declared.
        Attributes and valuables follow the keyword {\it attr} and {\it var} respectively.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller{
    call sMotor cMotor;
};
celltype tMotor{
    entry sMotor eMotor;
    attr{
        int32_t attr = 100;
    };
    var{
        int32_t var;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}

    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate {\it cell}s and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name such as tMotor, and a {\it cell} name such as Motor follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
        In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor{
};
cell tCaller Caller{
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

An mruby-TECS bridge plays a role to call a native program (e.g. C legacy code) from an mruby program.
The mruby-TECS bridge provides native libraries for mruby.
It also gives TECS components to receive the invocation from an mruby program.
The mruby-TECS bridge is described in more detail bellow.

As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{url:ASP}.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyontecs.pdf}
    \caption{System Model of existing mruby on TECS}
    \label{fig:mrubyontecs}
\end{figure}

@@

\section{mruby Bytecode Loader Using Bluetooth}
\label{sec:mruby bytecode loader using Bluetooth}
Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
    \caption{Detailed System Model of the proposed framework}
    \label{fig:system_model}
\end{figure}
This section describes an additional feature of mruby on TECS, mruby bytecode loader using Bluetooth.
In the current system, all binary data including bytecodes are in an SD card.
Developers must insert and pull out the SD card every time the source programs are modified.
The OS in the target device should be also restarted.
It causes a low work efficiency that such a work must be repeated.
mruby bytecode loader using Bluetooth makes the developers' burden decrease.
The work that an SD card is in and out needs to be done just once in the beginning.

@@

One of approaches for multitasking is co-routine.
Co-routine is a cooperative thread, and scheduled by developers with the functions such as {\it resume} and {\it yield}. 
(Ruby co-routine is defined in class Fiber \cite{url:co-routine})
Co-routine is a non-preemptive multitasking, and does not receive the OS's support because developers have to switch tasks manually.
Co-routine can not take advantage of multi core processing.

Besides, as another method, {\it delay}, a service call of $\mu$ITRON, can be used for multitasking.
This service call delays the execution of the own task for the time of the argument.
In the approach of {\it delay} function, developers have to schedule as the same as co-routine.

@@

\subsection{Component of Cyclic Handler}
Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
CyclicHandler {\it cell} configures the cyclic handler based on $\mu$ITRON.
Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
{\it rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
The attribute is used as an arguments of {\it rotateReadyQueue}.

Figure \ref{build_cyclic_handler} shows a build description that corresponds to the component diagram shown in Figure \ref{fig:cyclic_handler}.
In the part of CyclicHandler {\it cell}, configurations of a cyclic handler is described such as attribute, cyclicTime and cyclicPhase.
In this case, the cyclic handler is executed when it is generated because the attribute is {\it TA\_STA} that represents the cyclic handler is in an operational state after the creation.
The cyclic handler is executed every one msec.
In another part, the priority of CyclicMain {\it cell} is described.
RITEVM\_PRIORITY defines the priority of mruby tasks.
In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
If developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tCyclicHandler.cdl$>$);}.
This ease comes from component-based development with TECS.

@@

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
Multitasking's execution time is about the same as singletasking's while co-routine takes more time than them to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccccccc}
        & Bluetooth Loader & \shortstack{Call\\C function} & \shortstack{Legacy code of\\embedded system} & VM managenment & VM Scheduler & \shortstack{Synchronization of\\application} & Co-routine \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &            &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &            &            & \checkmark \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &            &            & \checkmark \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &            &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &            &            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparion}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in multi-VM.
Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
%%%%%%%%%%%%%
% Reference %
%%%%%%%%%%%%%
\bibliographystyle{IEEEtranBST2/IEEEtran}
\bibliography{ref}
